\section*{Data Types I}

\begin{aufgabe}[First steps, numbers]
Start the Python interpreter.
\begin{auflistung}
\item Use the online help: \lstinline{help()}, \lstinline{help(complex)}, \lstinline{dir(complex)}
\item Get familiar with the data types \texttt{int}, \texttt{float}, \texttt{complex} and the basic arithmetic operations.
\item What happens if you combine different data types in one calculation?
\item Display $1/3$ as a decimal $0.333333$\dots.
\item What is $1/0$?
\item Work with variable assignments. What happens if you successively assign objects of different data types to the same variable name?
\end{auflistung}
\end{aufgabe}

\begin{aufgabe}[Strings]
\begin{teilaufgabe}
Write a program which asks both for a user's given name and family  name. Afterwards, the program should print the full name and a greeting in one line, e.g.:
\begin{lstlisting}
Your given name? Jim
Your family name? Kirk
Live long and prosper, Jim Kirk
\end{lstlisting}
\end{teilaufgabe}

\newpage

\begin{teilaufgabe}
Extend the above program so that it additionally prints:
\begin{auflistung}
\item The letters 2 to 5 of the given name and the second to last letter of the family name.
\item The full name in capital letters.
\item Whether the name ends with "man".
\item \dots ? Try more string methods: \texttt{\underline{http://docs.python.org/lib/string-methods.html}}
\end{auflistung}
\end{teilaufgabe}
\end{aufgabe}

\begin{aufgabe}[Lists]
Start the Python interpreter.
\begin{auflistung}
\item Create a list with several elements and access those elements: The second element, the fourth to sixth elements, the last element. What happens if you use an invalid list index?
\item Add additional elements, delete elements. How does Python handle different data types in a list?
\item Join two lists.
\item Can you add a list as a list's element? How do you access elements of such a sublist?
\end{auflistung}
\end{aufgabe}

